Deliminative verbal reduplication in Mandarin Chinese

### 2025-07-30 replies-reviews2.tex

    \item The application of MRS within the HPSG framework represents a central focus of this paper. It might be helpful to explicitly acknowledge that the integration of MRS into the HPSG framework has been explored in prior research, such as \citet{Copestakeetal2005}. Addressing this would situate the current analysis more clearly within the broader theoretical landscape and strengthen its overall credibility.

    %%%%%%%%%%%%%%%%%%%
    %%%%%%%%%%%%%%%%%%%
    \noindent
    \textbf{Answer:} We added references and particularly mentioned that MRS is also used in other
    theoretical work and in computational implementations like the Grammar Matrix and CoreGram and
    we pointed the reader to the HPSG handbook, which has a section on MRS in the chapter on
    sematnics. We also point to Müller's forthcoming textbook that contains a chapter introducing
    MRS.

\end{enumerate}

\section{Shortening}
Since our manuscript exceeded the word limit of the journal, we moved the following parts into the appendices:
\begin{itemize}
    \item The analysis based on \citet{Tsai2008} (p. 25--27 in the last version of the manuscript), because \citet{YangWei2017} did not spell out the exact analysis, but only suggested that reduplication can be analyzed as an aspect marker in the aspectual system proposed by \citet{Tsai2008}. The analysis presented here is inferef by us based on \citet{Tsai2008}.

    \item The possible historical and phonological explanations for only \obj{yi} and \obj{le} appearing in between reduplication (footnote 17 in the last version of the manuscript).
\end{itemize}

### 2025-07-30 chapters/appendix.tex
move parts to appendix

\section{A new HPSG analysis}\label{sec:analysis}

In this section, we suggest a new lexical-rule-based analysis of aspect marking and reduplication
using Minimal Recursion Semantics (MRS; \citealt{Copestakeetal2005}). %, as proposed in \citet{LuMueller2021}.
MRS is one instance of underspecified semantics as is currently used in theoretical and
computational work in HPSG (\citealt[Section~6]{KR2024a}, \citealt[Section~3]{BFO2002a-u},
\citealt[Section~4.4]{MuellerCoreGram}, \citealt[Chapter~5]{MuellerLehrbuch4}). The advantage of
such types of semantics is that scope relations can be left underspecified. This way it is avoided
that large numbers of analyses are assigned to single sentences. Instead sentences are paired with
underspecified semantic representations from which various readings can be derived.
MRS uses lists of elementary predications that are connected via pointers. Scope constraints are
represented by statements of domination. This allows for elegant ways to underspecify scope. The
details cannot be discussed here. The interested reader is referred to \citet{Copestakeetal2005},
\citet[Section~6]{KR2024a} or for the use of MRS in a grammar of German to \citet[Chapter~5]{MuellerLehrbuch4}. In
what follows, we will present the elementary predications with the features assumed in MRS, but leave
out handle constraints to keep things simple.

Like \citet{FanSongBond2015}, we assume lexical rules for reduplication. Our lexical rules are
organized in an inheritance network. \textit{verbal-reduplication-lr} is the most general type for
reduplication lexical rules in this network and the implicational constraint in (\ref{avm:redup}) shows the constraints on all
structures of type \textit{verbal-reduplication-lr}. Such structures take a verb as
\textsc{lexical-daughter (lex-dtr)}.  The output reduplicates the \textsc{phonology (phon)} of the
input verb with the possibility to have further phonological material in between.  \etag{} indicates
an underspecified list which could be empty or not.\footnote{%
The \etag is equivalent to a tag with a number with the difference that \etag is never shared. We
follow Müller (\citeyear[161]{Mueller2002b}, \citeyear[294]{Mueller2003e}) and elsewhere in using this
notation, since we think this is more
precise than simply using three dots.}
A delimitative relation is appended to the
\textsc{relations (rels)} value of the input verb, and it takes the event index of the input verb \iboxb{3} as
argument (\textsc{arg0}, \ldots, \textsc{arg3} are feature names for arguments. The values are
indices or events similar to variables in normal predicate logic.). The list of relations contains so-called elementary predications. There is no complicated
embedding of relations. Instead each elementary predication comes with a label (\textsc{lbl}). The
label can be used as an argument of another relation or in scope constraints, which are not provided
here to keep things simple. The feature \textsc{ltop} points to the local top. This is the
elementary predication that is considered the top-most one in the \relsl. Other elementary
predications may share the label or have arguments with labels of other elementary predications. We
will discuss an example below when we discuss the perfective lexical rule.
The label of the output \iboxb{2} is identified with the label of the input and with the
label of the delimitative relation, hence \type{delimitative-rel} is treated as a modifier.  Further
relations can be added at the beginning of the \textsc{rels} list to allow for the additional
perfective meaning in A-\textit{le}-A and A-\textit{le}-\textit{yi}-A.  The combination with the
perfective will be elaborated on in the following paragraphs.

\eas
\type{verbal-reduplication-lr} \impl\\
%\scalebox{.9}{%
    \avm{
        [
        phon & \1 $\oplus$ \etag $\oplus$ \1\\
        synsem & [ loc\textbar cont [ ltop & \2 \\
        ind  & \3 ] ]\\
        rels & \etag $\oplus$ \4 $\oplus$ < [\type*{delimitative-rel}\\
        lbl & \2\\
        arg0 & \3 ] > \smallskip\\
        lex-dtr & [phon \1\\
        synsem\textbar loc & [cat  & [ head & verb ] \\
        cont & [ ltop & \2\\
        ind  & \3 ]]\\
        rels \4 ] ]
}
%}
\label{avm:redup}
\zs

To account for the variations in the phonology of the reduplication as well as 
the combination with the phonology and semantics of the perfective aspect marker \textit{le}, 
the type hierarchy of lexical rules in \figref{fig:typehi} is put forward. 
\begin{figure}
    \centering
    \scalebox{.9}{\begin{forest}
        type hierarchy
        [,phantom
        [,phantom
        [verbal-reduplication-lr,name=verbal-reduplicaiton-lr
        [non-perfective-reduplicaiton-lr
        [a-a-lr]
        [a-yi-a-lr]]
        [,identify=!r211]]]
        [aspect-marking-lr
        [perfective-lr
        [perfective-reduplicaiton-lr%,edge to=verbal-reduplicaiton-lr
        [a-le-yi-a-lr]
        [a-le-a-lr]]
        [v-le-lr]]
        [durative-lr]
        [\ldots]]]
    \end{forest}
}
    \caption{Type hierarchy for lexical rules of verbal reduplication and \textit{le}}
    \label{fig:typehi}
\end{figure}
Apart from the type \type{perfective-reduplication-lr}, 
which adds the inherited perfective relation, 
there is a subtype \type{non-perfective-reduplication-lr}, 
which does not add further relations. 
Hence, what is \etag in the \textsc{rels} list in (\ref{avm:redup}) is the empty list in (\ref{avm:nonperf}):
\ea\label{avm:nonperf}
\type{non-perfective-verbal-reduplication-lr} \impl\\
%\scalebox{.9}{%
    \avm{
        [
        rels & \1 $\oplus$ < [ ] > \smallskip\\
        lex-dtr & [ rels \1 ] ]
    }
%}
\z
The \textsc{rels} list of the output of the lexical rule is the \textsc{rels} list of
the daughter \iboxb{1} plus a list with one element. 
Since this element is specified in the supertype, it is not specified in (\ref{avm:nonperf}) again.

\type{non-perfective-verbal-reduplication-lr} has \type{aa-lr} and \type{a-yi-a-lr} as direct subtypes.
(\ref{avm:AA}) and (\ref{avm:AyiA}) show \type{aa-lr} and \type{a-yi-a-lr}, respectively.
As subtypes of \type{ver\-bal\hyp{}re\-dup\-li\-ca\-tion\hyp{}lr} illustrated in (\ref{avm:redup}), 
both inherit the constraints on the \textsc{lex-dtr} and on the semantics of the output, 
and because of (\ref{avm:nonperf}), no extra material is appended to the \textsc{rels} value of the input verb
and the list containing the \type{delimitative-rel}.
 In addition to the inherited constraints,
\type{aa-lr} and \type{a-yi-a-lr} specify the phonology of the output differently.
\type{aa-lr} determines that the \etag between the two phonological copies in (\ref{avm:redup}) is the empty list, 
whereas \type{a-yi-a-lr} specifies this list of phonological material as \phonliste{ yi }:

\ea\label{avm:constr-AA}
Constraints on lexical rules of type \type{aa-lr} and \type{a-yi-a-lr}:
%\begin{tabular}{@{}l@{\hspace{2cm}}l@{}}
 \ea   \type{aa-lr} \impl \\%& 
  %  \scalebox{.9}{%
        \avm{
            [phon & \1 $\oplus$ \1\\
            lex-dtr & [phon & \1] ]
    }
%} %& 
\ex	\type{a-yi-a-lr} \impl\\
 %    \scalebox{.9}{%
        \avm{
            [phon & \1 $\oplus$ \phonliste{ yi } $\oplus$ \1\\
            lex-dtr & [phon & \1] ]
    }
%}
%\end{tabular}
\z
\z

\noindent
The lexical rules with all inherited constraints are given in (\ref{avm:AA}) and (\ref{avm:AyiA}):

\ea\label{avm:AA}
The AA lexical rule with all constraints inherited from the supertypes:\\
%\scalebox{.9}{%
    \avm{
        [\type*{aa-lr}\\
        phon & \1 $\oplus$ \1\\
        synsem & [ loc\textbar cont [ ltop & \2 \\
        ind  & \3 ] ]\\
        rels & \4 $\oplus$ < [\type*{delimitative-rel}\\
        lbl & \2\\
        arg0 & \3 ] >\\
        lex-dtr & [phon & \1\\
        \punk{synsem\textbar loc}{[cat  & [ head & verb ]\\
            cont & [ ltop & \2\\
            ind  & \3 ]]}\\
        rels & \4]
        ]
}
%}
\z

%\newpage
\ea\label{avm:AyiA}
The A-\textit{yi}-A lexical rule with all constraints inherited from the supertypes:\\
%\scalebox{.9}{%
    \avm{
        [\type*{a-yi-a-lr}\\
        phon & \1  $\oplus$ \phonliste{ yi } $\oplus$ \1\\
        synsem & [ loc\textbar cont [ ltop & \2 \\
        ind  & \3 ] ]\\
        rels &  \4 $\oplus$ < [\type*{delimitative-rel}\\
        lbl & \2\\
        arg0 & \3 ] >\\
        lex-dtr & [phon & \1\\
        \punk{synsem\textbar loc}{[cat  & [ head & verb ]\\
            cont & [ ltop & \2\\
            ind  & \3 ]]}\\
        rels & \4]
        ]
}
%}
\z

\type{v-le-lr} is a direct subtype of the \type{perfective-lr}.
\type{perfective-reduplication-lr} inherits from both \type{verbal-reduplication-lr} and \type{per\-fec\-tive\hyp{}lr}
and has two subtypes, \type{a-le-yi-a-lr} and \type{a-le-a-lr} itself.
\type{verbal-reduplication-lr} is already presented in (\ref{avm:redup}). 
We now turn to the constraints on \type{perfective-lr} and its subtypes.

\citet[246]{MuellerLipenkova2013} propose the perfective lexical rule given in (\ref{avm:pfv-old}), 
adapted to the formalization adopted in the current paper.
It takes a verb as \textsc{lex-dtr}
and appends \phonliste{ le } to its phonology.
Further, it accounts for the change in semantics by appending the \textsc{rels} value of the input verb to a \type{perfective-rel}.

\ea\label{avm:pfv-old}
Perfective lexical rule adapted from \citet[246]{MuellerLipenkova2013}:\\
%\scalebox{.9}{%
    \avm{
        [\type*{perfective-lr}\\
        phon & \1 \+ \phonliste{ le }\\
        \punk{synsem\textbar loc\textbar cont}{ [ ltop & \2\\
            ind & \3 ]}\\ 
        rels & <[\type*{perfective-rel}\\
        lbl  & \2\\
        arg0 & \3\\
        arg1 & \4]> \,\+\, \5\smallskip\\
        lex-dtr & [phon & \1\\
        \punk{synsem\textbar loc}{[cat & [ head & verb]\\
            cont & [ ltop & \4\\
            ind & \3]]}\\
        rels & \5]
        ]
}
%}
\z
The event variables \iboxb{3} of the input and the output verb are shared. 
The \textsc{ltop} of the output of the lexical rule \iboxb{2} is the label of the perfective relation, 
and this relation scopes over the embedded verb. 
The handle of the embedded verb \iboxb{4} is the argument of the \type{perfective-rel}.

The lexical rule suggested in (\ref{avm:pfv-old}) only explains simple perfective aspect marking with \textit{le}, 
where \textit{le} immediately follows the verb.
But it cannot account for the perfective aspect marking of a reduplicated verb,
 as \textit{le} does not occur after the reduplication, 
nor can \textit{le} be reduplicated together with the verb.
It can only appear between the verb and the reduplicant.
In order to accommodate \textit{le} marking for both simple and reduplicated verbs, 
a general perfective lexical rule as in (\ref{avm:pfv-new}) and 
a subtype \type{v-le-lr} as in (\ref{avm:vle}) are posited here.
Besides adding a \type{perfective-rel} in the \textsc{rels} list of the output as in (\ref{avm:pfv-old}), 
the \type{perfective-lr} in (\ref{avm:pfv-new}) allows an underspecified list to be appended at the end of the \textsc{rels} list.
The \textsc{phon} value of the output makes it possible for further phonological material to occur both before and after \phonliste{ le }.

\ea\label{avm:pfv-new}
Type constraints on the type \type{perfective-lr} from which other subtypes inherit:\\
%\scalebox{.9}{%
    \avm{
        [\type*{perfective-lr}\\
        phon & \etag $\oplus$ \phonliste{ le } $\oplus$ \etag\\
        \punk{synsem\textbar loc \textbar cont}{ [ltop & \2\\
            ind  & \3]}\\ 
        rels & <[\type*{perfective-rel}\\
        lbl  & \2\\
        arg0 & \3\\
        arg1 & \4 ]> $\oplus$ \5 $\oplus$ \etag\smallskip\\
        lex-dtr & [%phon & \1\\
        \punk{synsem\textbar loc}{[cat & [ head & verb ]\\
            cont & [ ltop & \4\\
            ind  & \3]]}\\
        rels & \5]
        ]
}
%}
\z

\type{v-le-lr} with all inherited constraints as given in (\ref{avm:vle}) inherits from \type{perfective-lr} and specifies that the first element in the output \textsc{phon} list is identified with the \textsc{phon} value of the input verb
and that nothing else comes after \phonliste{ le }.
Furthermore, no other list can be appended at the end of the \textsc{rels} list of the output anymore.
This corresponds to the proposal of \citet[246]{MuellerLipenkova2013} shown in (\ref{avm:pfv-old}), 
which accounts for the simple perfective marking of verbs.

%\newpage
\ea\label{avm:vle}
Structure of type \type{v-le-lr} with constraints inherited from \type{perfective-lr}:\\
%\scalebox{.9}{%
    \avm{
        [\type*{v-le-lr}\\
        phon & \1 $\oplus$ \phonliste{ le }\\
        \punk{synsem\textbar loc \textbar cont\textbar ltop}{ \2}\\ 
        rels & <[\type*{perfective-rel}\\
        lbl  & \2\\
        arg0 & \3\\
        arg1 & \4]> $\oplus$ \5\smallskip\\
        lex-dtr & [phon & \1\\
        synsem\textbar loc \textbar cat  & [ head & verb\\
        cont & [ltop & \4\\
        ind & \3]]\\
        rels & \5]]
}
%}
\z

\type{perfective-reduplication-lr} inherits from both \type{verbal-reduplication-lr} and \type{per\-fec\-tive\hyp{}lr}.
The \textsc{phon} value of the output reduplicates the phonology of the input verb and states that there is \phonliste{ le } in between, 
as well as potentially further phonological material.
The \textsc{rels} list of the output appends the \type{delimitative-rel} to the \type{perfective-rel} and the \textsc{rels} value of the input verb.
The arguments of both \type{perfective-rel} and \type{delimitative-rel} share the event index of the
input verb \iboxb{3} to ensure that they apply to the same event denoted by the input verb. 
The label of the \type{delimitative-rel} and the input verb are identified (\type{delimitative-rel} is a modifier) 
and this shared label is embedded under the \type{perfective-rel}.

\ea\label{avm:pfv-redup}
Perfective and reduplication combined: type \type{perfective-reduplication-lr} with
constraints inherited from \type{perfective-lr} and \type{verbal-redu\-pli\-ca\-tion-lr}:\\
%\resizebox{\linewidth}{!}{
 %   \scalebox{.9}{%
        \avm{
            [\type*{perfective-reduplication-lr}\\
            phon & \1 $\oplus$ \phonliste{ le } $\oplus$ \etag $\oplus$ \1\\
            \punk{synsem\textbar loc\textbar cont\textbar ltop}{ \2}\\ 
            rels & <[\type*{perfective-rel}\\
            lbl & \2\\
            arg0 & \3\\
            arg1 & \4]>
            $\oplus$ \5 $\oplus$
            <[\type*{delimitative-rel}\\
            lbl  & \4\\
            arg0 & \3]>\\
            lex-dtr & [phon & \1\\
            synsem\textbar loc & [cat  & [ head & verb ]\\
            cont & [ ltop & \4\\
            ind  & \3]]\\
            rels & \5]
            ]
    }
%}
    %}
\z
For example %(\ref{ex-he-tasted-the-soup-a-little-bit}), repeated here as
 (\ref{ex-he-tasted-the-soup-a-little-bit2}), we get the  MRS representation in (\ref{ex:mrs-soup}),
where h1 and h2 correspond to the handles \ibox{2} and \ibox{4} and e1 to the event variable \ibox{3}:
\ea\label{ex-he-tasted-the-soup-a-little-bit2}
    \gll \objex{ta1} \obj{chang2}-\obj{le}-\obj{chang2} \objex{tang1}.\\
    he taste-\textsc{pfv}-taste soup\\
    \glt `He tasted the soup a little bit.'
 \z
\ea\label{ex:mrs-soup}
h1 \sliste{ h1:perfective(e1,h2), h2:taste(e1,he,soup), h2:delimitative(e1) }
\z
So the delimitative relation is treated as an adjunct to the main relation of the verb, 
and the perfective relation scopes over both the main relation and the delimitative relation.

Two subtypes of \type{perfective-reduplication-lr} are posited:
\type{a\hyp{}le\hyp{}yi\hyp{}a\hyp{}lr} %as in (\ref{avm:AleyiA}) 
and \type{a-le-a-lr}, as shown in (\ref{avm:AleA}). %(\ref{avm:AleA}).
They take over the semantic change to the input from \type{perfective\hyp{}reduplication\hyp{}lr}, but specify the \textsc{phon} value differently.
Specifically, \type{a\hyp{}le\hyp{}yi\hyp{}a\hyp{}lr} specifies the middle phonological material as
\phonliste{ le, yi }, while \type{a-le-a} specifies it as \phonliste{ le } only.\footnote{
A reviewer wants to know what prevents phonological material other than \obj{yi} and \obj{le} to appear in between the reduplicated elements.
He/she states that this aspect seems to be somewhat arbitrary, and it is not evident why certain elements are permissible while others are not.

@@

The subtypes of \type{verbal-reduplication-lr} (\ref{avm:AyiA}, \ref{avm:AleA}) prevent phonological materials other than \phonliste{ le } and \phonliste{ yi } from appearing in between the reduplication by specifying what can appear in the \etag list and what not.
}

\ea\label{avm:AleA}
%\begin{tabular}{@{}l@{\hspace{2cm}}l@{}}
\ea    %\scalebox{.9}{%
        \type{a-le-yi-a-lr} \impl\\
        \avm{
            [%\type*{a-le-yi-a-lr}\\
            phon & \1 \+ \phonliste{ le, yi } \+ \1\\
            lex-dtr & [phon & \1
            ]
            ]
    }
%}%&
\ex   % \scalebox{.9}{%
\label{avm:a-le-a-lr}
    \type{a-le-a-lr} \impl\\
        \avm{
            [%\type*{a-le-a-lr}\\
            phon & \1 \+ \phonliste{ le } \+ \1\\
            lex-dtr & [phon & \1
            ]
            ]
    }
%}
%\end{tabular}
\z
\z

The analysis of (\ref{ex-he-tasted-the-soup-a-little-bit2}) is shown in tree format in
Figure~\ref{fig-he-tasted-the-soup-a-little-bit}. The \textsc{lex-dtr} is the daughter in the tree.
\begin{figure}[htbp]
\centering
\begin{forest}
[        \avm{
            [\type*{a-le-a-lr}\\
            phon & \1 $\oplus$ \phonliste{ le } $\oplus$ \1\\
            synsem\textbar loc & [ cat  & [ head  & verb\\
                                            spr   & < NP$_{\6}$ >\\
                                            comps & < NP$_{\7}$ > ]\\
                                   cont & [ ltop & \2\\
                                            ind  & \ibox{3} ]] \\
            rels & <[\type*{perfective-rel}\\
            lbl & \2\\
            arg0 & \3\\
            arg1 & \4]> $\oplus$ \5 $\oplus$
            <[\type*{delimitative-rel}\\
            lbl  & \4\\
            arg0 & \3]> ]
    }
[\avm{ [phon & \1 \phonliste{ chang2 }\\
       synsem\textbar loc & [cat  & [ head  & verb\\
                                      spr   & < NP$_{\6}$ >\\
                                      comps & < NP$_{\7}$ > ]\\
                             cont & [ ltop & \4\\
                                      ind  & \3]]\\
        rels & \5 < [\type{taste}\\
                     lbl  & \4\\
                     arg0 & \3\\
                     arg1 & \6\\
                     arg2 & \7 ] > ]
}]]
\end{forest}

\caption{Analysis of \obj{chang2-le-chang2} taste-\textsc{pfv}-taste `taste the soup a little bit'}\label{fig-he-tasted-the-soup-a-little-bit}
\end{figure}

The figure shows how the lexical item for \obj{chang2} `to taste' is inserted as a daughter into
the \type{a-le-a-lr} lexical rule. The arguments of \obj{chang2} `to taste' are represented within the \spr and
the \compsl (see \citealt{GSag2000a-u} for English) and the respective argument NPs are linked to the
arguments of \type{taste}: the subject is \textsc{arg1}, the agent, and the object is \textsc{arg2},
the stimulus. See \citet{DKW2021a} for more on linking. The part of speech of the lexical item
(\type{verb}) and the valence information is carried over from the daughter to the mother
unchanged. The semantic contribution of the daughter verb, the value of \ibox{5}, is inserted into
the \relsl of the mother as it was specified in the constraints on the type
\type{perfective-reduplication-lr} in (\ref{avm:pfv-redup}). The \textsc{phon} value of the mother
is the concatentation of \obj{chang2}, \obj{le} and \obj{chang2}, as specified in the constraint
on \type{a-le-a-lr} in (\ref{avm:a-le-a-lr}). The resulting unit \obj{chang2-le-chang2} then
combines with its object forming a VP. This VP is combined with the subject resulting in a complete
verbal projection, a sentence. \obj{chang2-le-chang2} behaves in the same way as the simple \obj{chang2}.

Since the above-described lexical rules do not constrain the number of syllables of the input verb, but simply reduplicate its phonology  as a whole,
they can also account for the ABAB and the AB-\textit{le}-AB forms of reduplication,
as long as the input verb is disyllabic.
Notice that  the lexical rules above also produce AB-\textit{yi}-AB and AB\hyp{}\textit{le}\hyp{}\textit{yi}\hyp{}AB for disyllabic input verbs.
Although these forms are considered unacceptable by some authors \citetext{\citealp[30]{LiThompson1981}; \citealp[275--276]{Hong1999};  \citealp[160]{BascianoMelloni2017}; \citealp[239]{YangWei2017}}, 
\citet[269]{Fan1964} and \citet[143]{Sui2018} consider AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB to be possible, even though they both recognize that these two forms are rare.
Indeed, a few examples of AB\hyp{}\emph{yi}\hyp{}AB and AB\hyp{}\emph{le}\hyp{}\emph{yi}\hyp{}AB in Early Mandarin %(12th to 20th centuries)
 (\ref{ex:AByiAB-lu}--\subref{ex:AByiAB-pu}) and Modern Mandarin (\ref{ex:AByiAB-rou1}--\subref{ex:ABleyiAB-ccl}) were found.

\settowidth\jamwidth{(CCL)}

\begin{sloppypar}
\ea\label{ex:ABleyiAB}
\ea\label{ex:AByiAB-lu}
\gll \objex{ni3} \objex{yu3} \objex{wo3} \obj{zheng3li3-yi-zheng3li3}.\footnotemark\\
you let me arrange-one-arrange\\
\glt `Let me arrange it a little bit!'
\footnotetext{\obj{Yuan2qu3} \obj{xuan3}: \obj{Lu3zhai1lang2} \textit{[Selected Yuanqu: Luzhailang]}, as cited in \citet[15]{Zhang2000}}

\ex\label{ex:AByiAB-pu}
\gll \objex{ni3} \obj{da3ting1-yi-da3ting1}.\footnotemark\\
you inquire-one-inquire\\
\glt `Inquire about it a little bit!'
\footnotetext{\obj{Yuan2} \obj{Ming2} \obj{juan4}: \obj{Piao2tong1shi4} \textit{[Yuan and Ming volume: Piaotongshi]}, 308, as cited in \citet[15]{Zhang2000}}

\ex\label{ex:AByiAB-rou1}
\gll \objex{ge4} \objex{ge4} \objex{dian3-tou2} \obj{wei1xiao4-yi-wei1xiao4}.\footnotemark\\
\textsc{clf} \textsc{clf} nod-head smile-one-smile\\
\glt `Each one nodded his head and smiled a little bit.'
\footnotetext{\objex{Rou2}, \objex{Shi2}. 1975. \obj{Rou2} \obj{Shi2} \obj{xiao3shuo1} \obj{xuan3ji2} \textit{[Selected novels of Roushi]}, 31. Beijing: People's Literature Publishing House.}

\ex\label{ex:AByiAB-rou2}
\gll \objex{ta1} \obj{wei1xiao4-le-yi-wei1xiao4}, you \obj{ming2xiang3}-\obj{le-yi}-\obj{ming2xiang3}.\footnotemark\\
he smile-\textsc{pfv}-one-smile and meditate-\textsc{pfv}-one-meditate\\
\glt `He smiled a little bit and meditated a little bit.'
\footnotetext{\objex{Rou2}, \objex{Shi2}. 1975. \obj{Rou2} \obj{Shi2} \obj{xiao3shuo1} \obj{xuan3ji2} \textit{[Selected novels of Roushi]}, 31. Beijing: People's Literature Publishing House.}

\ex\label{ex:AByiAB-li}
\gll \objex{fei1chang2} \objex{yan2su4} de \objex{ba3} \objex{jin4shi4} \objex{yan3jing4} \obj{duan1zheng4-le-yi-duan1zheng4}.\footnotemark\\
very seriously \textsc{de} \textsc{ba} nearsighted glasses straighten-\textsc{pfv}-one-straighten\\
\glt `[He] very seriously straightened the nearsighted glasses quickly.'
\footnotetext{\objex{Li3}, \objex{Jie2ren2}. 1962. \obj{Da4} \obj{bo1} \textit{[Great wave]}, 3rd band, 171. Beijing: The Writers Publishing House.}

\ex\label{ex:ABleyiAB-ccl}
\gll \objex{ji3duo1} \objex{san3luan4}-zhe de \objex{chuan2} \objex{li3} de \objex{deng1guang1}, \objex{ye3} \objex{hu1yin1hu1mie4} de \obj{bian4huan4-le-yi-bian4huan4} \objex{wei4zhi}.\\
many scattered-\textsc{dur} \textsc{de} boat in \textsc{de} light also flicker \textsc{de} change-\textsc{pfv}-one-chang position\\ \jambox{(CCL)}
\glt `Many scattered lights in the boats also changed their positions a little bit, flickering.'
\z
\z
\end{sloppypar}

This suggests that  even though AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB might be degraded, they are not ungrammatical \textit{per se}.
The reason for this degradedness is probably phonological, since AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB contain too many syllables \citetext{\citealp[274]{Fan1964}; \citealp[15]{Zhang2000}; \citealp[239]{YangWei2017}; \citealp[143]{Sui2018}}, but we argue that it is not an issue of grammaticality.
Thus, they can still be produced via the lexical rules posited above, but are ruled out or degraded due to a general phonological constraint.\footnote{
One reviewer suggests that given that AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB were possible in previous stages of the language (see \citealt[15]{Zhang2000}, \citealt[160--161]{BascianoMelloni2017}),
these rare occurrences can be seen as relics of this usage.
}

AAB, A-\textit{yi}-AB, A-\textit{le}-AB, AA-\obj{kan4} and A-\obj{kan4}-\obj{kan4} can also be accounted for by the lexical rules proposed in this section.
They can be analyzed as compounds consisting of a reduplicated monosyllabic verb and another element.
Specifically, AAB, A-\textit{yi}-AB and A-\textit{le}-AB can be considered as the compound of a reduplicated monosyllabic verb (A) and a noun (B).\footnote{
    \citet[64--65]{Huang1984} and \citeauthor{Her1996} (\citeyear[Sec.\,2]{Her1996}; \citeyear[Sec.\,3.1]{Her2010}) argue that some of these V-O combinations are compounds, some are phrases, and some have dual status (both compounds and phrases).
    Following this approach, AAB, A-\textit{yi}-AB and A-\textit{le}-AB can (also) be considered as the phrasal combination of a reduplicated verb and its object.
}
AA-\obj{kan4} can be regarded as the compound of a reduplicated monosyllabic verb (A) and the verb \obj{kan4} `look',
whereas A-\obj{kan4}-\obj{kan4} is the compound of a monosyllabic verb (A) and the reduplication of \obj{kan4} `look'.
A-\obj{yi}-A-\obj{kan4} is also possible, though rare, presumably also due to its length.
An inquiry in CCL found 55 hits of A-\obj{yi}-A-\obj{kan4}.
A sample is listed in (\ref{ex:AyiAkan}).

\begin{sloppypar}
\ea\label{ex:AyiAkan}
\ea
\gll \objex{te4yi4} \objex{gong1neng2} de \objex{yan2jiu1zhe3}-men \objex{bu4fang2} \objex{ru2ci3} \obj{shi4-yi-shi4-kan4} \ldots\\
special power \textsc{de} researcher-\textsc{pl} may.as.well such try-one-try-look\\ \jambox{(CCL)}
\glt `Researchers of special power may as well have a try as such and see \ldots'

>>>>

\section{Analysis based on the aspectual system by \citet{Tsai2008}}\label{app:tsai}

\citet[229]{YangWei2017} claim that reduplication can be analyzed as an aspect marker 
following the structure of Mandarin Chinese aspects proposed by \citet{Tsai2008}.
 \citet{Tsai2008} provides the syntactic analysis for aspect markers in Mandarin Chinese as shown in \figref{tree:tsai}.\footnote{Asp = Aspect}
He observes the so-called incompleteness effect, namely that a minimal sentence, 
which only contains a verb marked by \obj{zhe} `\textsc{dur}',
\obj{le} `\textsc{pfv}' or \obj{wan2} `\textsc{compl}' 
and its arguments, 
seems incomplete without further sentential elements 
such as the sentence final particle \obj{le} 
or a temporal adverbial like \obj{gang1cai2} `just now' (\ref{ex:incomplete}). 
In contrast, a minimal sentence with a verb marked by  \obj{zai4} `\textsc{prog}' or \obj{guo}
`\textsc{exp}'  and its arguments can stand alone (\ref{ex:complete}).

\ea\label{ex:incomplete}
\gll \objex{Xiao3li3} \objex{chi1}-zhe/le/\objex{wan2} \objex{fan4} *(le).\\
Xiaoli eat-\textsc{dur}/\textsc{pfv}/\textsc{compl} meal \textsc{ptc}\\
\glt `Xiaoli is eating/ate/finished eating the meal.'
\z

\ea\label{ex:complete}
\gll \objex{Xiao3li3} (\objex{gang1cai2}) \objex{zai4} \objex{ku1}/\objex{ku1}-\objex{guo}.\\
Xiaoli just.now \textsc{prog} cry/cry-\textsc{exp}\\
\glt `Xiaoli was crying/cried just now.'
\z
He thus proposes three aspect positions under TP. \obj{zai4} `\textsc{prog}' and \obj{guo} `\textsc{exp}' reside under Asp$_1$, 
while \obj{zhe} `\textsc{dur}' and \obj{le} `\textsc{pfv}' under Asp$_2$, as illustrated in \figref{tree:tsai}.\footnote{
    \citet{Tsai2008} differentiated the middle and the inner aspect based on the fact that 
    \obj{wan2} can only occur with certain types of predicate.
    This differentiation does not play a role for our purpose and will not be further discussed here.}

\begin{figure}
    \centering
    \begin{forest}
        [TP [T]
        [...
        [AspP$_1$ (outer aspect) [Asp$_1$\\\obj{zai4/guo}]
        [\textit{v}P [\textit{v}]
        [AspP$_2$ (middle aspect) [Asp$_2$\\\obj{zhe/le}]
        [VP [V-Asp$_3$ (inner aspect)\\\obj{wan2}]
        ]
        ]
        ]
        ]
        ]
        ]
    \end{forest}
    \caption{Structure of the aspectual system in Mandarin Chinese according to \citet[683]{Tsai2008}}
    \label{tree:tsai}
\end{figure}

Turning to reduplication, a minimal sentence with reduplication also seems incomplete (\ref{ex:redup-tsai}).
Based on this, the reduplicant should reside under Asp$_2$, as illustrated in \figref{tree:redupasp}.

\ea\label{ex:redup-tsai}
\ea[*] {\gll \objex{ta1} \obj{xiao4}-\obj{xiao}\\
    he laugh-laugh\\}
\ex[] {\gll \objex{ta1} \obj{xiao4}-\obj{le}-\obj{xiao4}\\
    he laugh-\textsc{pfv}-laugh\\
    \glt `He laughed a little.'}
\ex[] {\gll \objex{ta1} \obj{xiao4}-\obj{xiao}, \objex{bu4} \objex{shuo1hua4}\\
    he laugh-laugh not speak\\
    \glt `He laughed a little, and didn't speak.'}\label{ex:redup-tsai-co}
\z
\z

\begin{figure}
    \centering
    \begin{forest}
        [TP [T]
        [...
        [AspP$_1$ (outer aspect) [Asp$_1$\\\obj{zai4/guo}]
        [\textit{v}P [\textit{v}]
        [AspP$_2$ (middle aspect) [Asp$_2$\\\obj{zhe}/\obj{le}/reduplication]
        [VP [V-Asp$_3$ (inner aspect)\\\obj{wan2}]
        ]
        ]
        ]
        ]
        ]
        ]
    \end{forest}
    \caption{Position of reduplication according to the aspectual system in \citet{Tsai2008}}
    \label{tree:redupasp}
\end{figure}

This analysis would result in a mismatch between syntax and semantics, 
in the sense that the aspect markers that belong to the same semantic group do not occur in the same syntactic position. 
Even though \obj{le} `\textsc{pfv}', \obj{guo} `\textsc{exp}' and reduplication all mark perfective aspects (\sectref{sec:aspM}, \citealt{Dai1997, XiaoMcEnery2004}),
\obj{guo} `\textsc{exp}' is situated under Asp$_1$, while \obj{le} `\textsc{pfv}' and reduplication are under Asp$_2$.
Similarly, \obj{zai4} `\textsc{prog}' and \obj{zhe} `\textsc{dur}' are both imperfective aspects but also occur in different syntactic positions.

\section{\obj{yi} and \obj{le}}\label{app:hist}
A reviewer suggests that 
the fact that only  \obj{yi} and \obj{le}  can appear in between reduplication 
seems somewhat arbitrary, 
and it is not evident why certain elements are permissible while others are not.
We think that there might be historical and phonological reasons.

@@

%The subtypes of \type{verbal-reduplication-lr} (\ref{avm:AyiA}, \ref{avm:AleA}) prevent phonological materials other than \phonliste{ le } and \phonliste{ yi } from appearing in between the reduplication by specifying what can appear in the \etag list and what not.
